QSS27: Revision II

### 2019-09-15 Revision2Letter.tex
Bradley's suggestion

@@

\item Nevertheless, the reference count issue raised is interesting in itself (although it is not quite clear what is meant by signal) so we have added a sentence to the Discussion addressing it. The reviewer argues that 10 references (45 z-scores/article) would be a reassuring number. This choice appears intuitive rather than reasoned. We chose to set the threshold at 2 references since it is the smallest number that yields a reference pair. This threshold also supports comparison with Uzzi's data. It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores. Lastly, there is a penalty for arbitrarily excluding low-reference publications. For example, restricting the applied physics dataset from 1985 (ap\_1985) to publications with 5 references or less results in a loss of 28\% of the publications and associated references.

>>>>

In fact, what began as a simple experiment turned out to be quite complicated and out of scope for this article. We have modified the Discussion to make this point.

@@

\item Nevertheless, the reference count issue raised is interesting in itself (although it is not quite clear what is meant by signal) so we have added a sentence to the Discussion addressing it. The reviewer argues that 10 references (45 z-scores/article) would be a reassuring number. This choice appears intuitive rather than reasoned. In our manuscript, we chose to set the threshold at 2 references since it is the smallest number that yields a reference pair. This threshold also supports comparison with Uzzi's data. It is perhaps useful to be reminded that these reference pairs are then mapped to journal pairs whose frequencies are summed across the dataset being studied, then normalized, and finally returned to the parent article as z-scores. Lastly, there is a penalty for arbitrarily excluding low-reference publications. For example, restricting the applied physics dataset from 1985 (ap\_1985) to publications with 5 references or less results in a loss of 28\% of the publications and associated references. For the two biology-baed datasets recovery of between 92-95 \% of the publications we analyzed occurs when a cutoff of 10 references is applied. For the applied\_physics dataset, which has different citation and reference characteristics, we would recover between 45-69\% for the three years we studied. For the complete WoS set, recovery ranges between 63-77\%. This is not surprising, we expect disciplinary differences but a cutoff value of 10 references has different effects that need to be carefully studied along with the other variables that contribute to citation counts.
